\section*{業績一覧}

\subsection*{査読論文}
\begin{enumerate}
\item Fukushima, K., Uchida, N., and Okada, K. (2024-05-06). Modeling Partial Knowledge in Multiple-Choice Cognitive Diagnostic Assessment. \textit{Journal of Educational and Behavioral Statistics}, OnlineFirst. DOI: \href{https://doi.org/10.3102/10769986241245707}{10.3102/10769986241245707}
\item 福島健太郎・内田菜緒・岡田謙介 (2021). Q 行列を付与した多枝選択形式テストの開発ー認知診断モデルのための英語の空所補充問題の作成ー. \textit{日本テスト学会誌}, 17(1), 45--59. DOI: \href{https://doi.org/10.24690/jart.17.1_45}{10.24690/jart.17.1_45}
\end{enumerate}

\subsection*{preprint}
\begin{enumerate}
\item Fukushima, K., Uchida, N., and Okada, K. (2023-07-24). Modeling Partial Knowledge in Multiple-Choice Cognitive Diagnostic Assessment. \textit{Open Science Framework}, . DOI: \href{https://doi.org/10.31234/osf.io/wefb7}{10.31234/osf.io/wefb7}
\end{enumerate}

\subsection*{国際学会における発表（査読あり）}
\begin{enumerate}
\item  Oral Fukushima, K., Higashiguchi, R., and Okada, K.. \textit{Refinement of the Matching Item Response Model: A Shift to Generative Modeling}, International Meeting of Psychometric Society (IMPS), Prague.
\item  Oral Okada, K. and Fukushima, K.. \textit{Partial-knowledge models for cognitive diagnosis: Formulations, consistency, and relation to other models}, Australasian Mathematical Psychology Conference (AMPC), Perth.
\item  Oral Fukushima, K. and Okada, K.. \textit{A novel framework of diagnostic classification model for multiple-choice items and a simulation study.}, International Meeting of Psychometric Society (IMPS),, Maryland.
\item  Oral Fukushima, K. and Okada, K.. \textit{Multiple-choice log-linear cognitive diagnostic model framework and its application.}, Computational and Methodological Statistics (CMStatistics), London.
\item  Oral Fukushima, K., Uchida, N., and Okada, K.. \textit{Modeling partial knowledge in multiple-choice cognitive diagnostic models.}, International Meeting of Psychometric Society (IMPS), Online.
\end{enumerate}

\subsection*{招待セッショントーク（Invited Session Talk）}
\begin{enumerate}
\item [Invited] Oral Fukushima, K. and Okada, K.. \textit{A generalized class of cognitive diagnostic models for multiple-choice items derived from the log-linear model.}, The 11th Conference of the Asian Regional Section of the International Association for Statistical Computing (IASC-ARS), Online.
\end{enumerate}

\subsection*{国内学会・シンポジウム等における発表}
\begin{enumerate}
\item  口頭 福島健太郎・岡田謙介. {一般化多枝選択型認知診断モデルの提案}, 日本計算機統計学会 第37回シンポジウム, 宮崎.
\item  口頭 福島健太郎・岡田謙介. {消去法を考慮した多枝選択型認知診断モデルによる実証分析}, 日本計算機統計学会 第34回シンポジウム, 学生研究発表セッション2-3, オンライン開催.
\item  ポスター 福島健太郎・上淵寿. {ガウスフィルタと共感性が表情認知の正確性に及ぼす影響}, 日本心理学会 第84回大会, PI-037, オンライン開催.
\item  ポスター 上淵寿・福島健太郎. {アタッチメントの潜在不安的側面とネガティブ感情喚起が潜在的情動制御に及ぼす影響}, 日本心理学会 第84回大会, PM-005, オンライン開催.
\item  口頭 福島健太郎・岡田謙介. {消去法を反映した多枝選択型認知診断モデル}, 日本行動計量学会 第48回大会特別セッション(対面開催中止に伴い，抄録での掲示のみ), C4-4, オンライン開催.
\item  口頭 福島健太郎. {多枝選択CDMにおける消去方略のモデリング}, 日本計算機統計学会若手セミナー2020, 発表6, オンライン開催.
\end{enumerate}


